Changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh

### 2020-10-23 Frequency-of-Travel-by-Mode-COVID-19-Bangladesh/Frequency-of-Travel-by-Mode-COVID-19-Bangladesh.Rmd
shaila

---
title: An exploratory analysis of changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh
author:
  - name: Shaila Jamal
    email: jamals16@mcmaster.ca
    affiliation: McMaster University
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
address:
  - code: McMaster University
    address: School of Earth, Environment and Society, McMaster University, Hamilton, ON, L8S 4K1, Canada
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
 The COVID-19 pandemic has had a profound impact on mobility in every country and region around the world. Recent helps to illuminate some of the dimensions of change - however, the evidence is still scant in developing countries. The objective of this paper is to present an exploratory analysis of the changes in the frequency of trip-making by mode during the COVID-19 emergency in Bangladesh. The results confirm an overall loss of mobility in the form of reduced trip-making frequency by all modes, but the changes are not uniform across modes. In particular, there was a greater loss of mobility for bus, rickshaw, and CNG auto-rickshaw.

@@

Data used for this paper come from an online survey, "Exploring the potential of travel mode change behavior in the post-lock-down and post-pandemic (COVID-19) period" conducted during July - August 2020 in Bangladesh. The survey was available both in Bengali and English and disseminated through various electronic means along with a widespread social media campaign and promotion in various social media sites and groups. In addition to socio-economic and demographic information of the respondents, the survey covered different aspects of travel such as travel behavior before and during COVID-19, knowledge related to COVID-19, and opinions and perceptions regarding travel behavior after lock-down and post-pandemic situation.

>>>>

---
title: Changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh
author:
  - name: Shaila Jamal
    email: jamals16@mcmaster.ca
    affiliation: McMaster University
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
address:
  - code: McMaster University
    address: School of Earth, Environment and Society, McMaster University, Hamilton, ON, L8S 4K1, Canada
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
 The COVID-19 pandemic has had a profound impact on mobility in every country and region around the world. Recent studies help to illuminate some of the dimensions of change - however, the evidence is still scant in developing countries. The objective of this paper is to present an exploratory analysis of the changes in the frequency of trip-making by mode during the COVID-19 emergency in Bangladesh. The results confirm an overall loss of mobility in the form of reduced trip-making frequency by all modes, but the changes are not uniform across modes. In particular, there was a greater loss of mobility for bus, rickshaw, and CNG auto-rickshaw, and some adoption of walking during the pandemic.

@@

Data used for this paper come from an online survey, "Exploring the potential of travel mode change behavior in the post-lock-down and post-pandemic (COVID-19) period" conducted during July - August 2020 in Bangladesh. The country was under partial lock-down during the survey period where essential services remained open, offices were running on rotation basis, all educational institutes were closed and public transport services were running at 50% capacity. The survey was disseminated through various electronic means along with a widespread social media campaign and promotion in various social media sites and groups. In addition to socio-economic and demographic information of the respondents, the survey covered different aspects of travel such as travel behavior before and during COVID-19, knowledge related to COVID-19, and opinions and perceptions regarding travel behavior after lock-down and post-pandemic situation.
